Abstract

### 2025-05-22 output/Letter_to_editor_reviewers.Rmd
Explain misuse of "indistinctly"

This is the expression of a vector represented in a basis, in this case, representing that the vector can be represented in each of the two bases indistinctly.
Following the reviewer's suggestion, we have added this clarification to the text, so it now reads:

@@

<!-- # TODO: Add response -->

>>>>

This is the expression of a vector represented in a basis, in this case, representing that the vector can be represented in each of the two bases interchangeably.
Following the reviewer's suggestion, we have added this clarification to the text, so it now reads:

@@

This is a mistake on our side, we are afraid to admit, product of a careless translation of a false friend from our mother tongue Spanish ("indistintamente"), which means "indifferently".
We have changed the term by the mathematically appropriate "interchangeably" in our new version.
